### 2021-05-12 proposal/proposal.Rmd
updated proposal

options(xtable.comment = FALSE, 
        xtable.table.placement = 'H')
```

@@

Graph and network data have become increasingly widespread in various fields including sociology, neuroscience, biostatistics, and computer science. This has resulted in various challenges for researchers who rely on traditional statistical and machine learning methods, many of which are incompatible with graph data and instead require the data to exist as feature vectors in Euclidean space. Such challenges often involve clustering and community detection. Common clustering methods typically involve calculating some central or representative point for each cluster around which the data belonging to that cluster lie (e.g., Lloyd's algorithm for $K$-means clustering \cite{1056489}, Gaussian Mixture Models \cite{doi:10.1198/016214502760047131}). Because these methods involve computing summary statistics within each cluster, such as the sample average, they cannot be applied directly to graphs, necessitating methods for transforming the graph data into feature vectors.

@@

The aim of our research is to develop consistent community detection techniques under the RDPG and GRDPG frameworks. First, we explore existing generative graph models with underlying community structures that can be inferred by connecting the generative models to the RDPG or GRDPG. Then we explore other latent structures or mixture distributions in the latent space that induce graphs for which consistent community detection is possible.

@@

Let $G = (V, E)$ be an undirected, unweighted graph with no self-loops with $n$ vertices. Denote $A \in \{0, 1\}^{n \times n}$ as the adjacency matrix for $G$ such that $A_{ij} = 1$ if there exists an edge between vertices $i$ and $j$ and $A_{ij} = 0$ otherwise. Because $G$ is symmetric and contains no self-loops, $A_{ij} = A_{ji}$ and $A_{ii} = 0$ for $i, j \in [n]$. We further restrict our analyses to independent Bernoulli graphs. Let $P \in [0, 1]^{n \times n}$ be a symmetric matrix of edge probabilities. Graph $G$ is sampled from $P$ by drawing $A_{ij} \indep \Bernoulli(P_{ij})$ for each $0 \leq i < j \leq n$ ($A_{ji} = A_{ij}$ and $A_{ii} = 0$). Finally, we denote $X = \begin{bmatrix} x_1 & \cdots & x_n \end{bmatrix}^\top \in \mathbb{R}^{n \times d}$ as the sample $x_1, ..., x_n \in \mathbb{R}^d$, and denote $z_1, ..., z_n \in [K]$ as their corresponding (hidden) labels.

@@

Generative models for symmetric Bernoulli graphs involve defining the edge probability matrix $P$ whose $ij$^th^ entry is the probability of an edge between vertices $i$ and $j$ for each $i, j \in [n]$. In order to motivate community detection methods, we restrict the generative model such that for each pair of vertices, the probability of an edge between the vertices is conditioned on the labels of the vertices. One such model is the Stochastic Block Model (SBM) \cite{doi:10.1080/0022250X.1971.9989788}: Given $K$ communities and each vertex belonging to one community, the SBM restricts $P$ to $K (K + 1) / 2$ unique entries such that $P_{ij} = B_{z_i z_j}$ and $B \in [0, 1]^{K \times K}$ with entries $B_{kl}$ denoting the edge probability of each vertex in community $k$ having an edge with each vertex in community $l$. The homogeneous SBM further restricts $P$ to two unique entries such that $P_{ij} = p$ if $z_i = z_j$ and $P_{ij} = q$ otherwise. Multiple generalizations of the SBM have been introduced since, including the Degree Corrected Block Model (DCBM) and the Popularity Adjusted Block Model (PABM). Like the SBM, these models involve edge probability matrix $P$ that is restricted to rank $d < n$ in part based on community labels.

@@

The structure of the RDPG and GRDPG provides a straightforward method for recovery of the latent positions via spectral embedding.

@@

It is straightforward to show that all Bernoulli graphs with positive semidefinite $P$ are special cases of the RDPG, which is a special case of the GRDPG, and all graphs generated by $P$ are special cases of the GRDPG. This includes the SBM, DCBM, and PABM. In the following example, we show that the ASE of the SBM has a very particular form.

\begin{example}[Connecting the SBM to the RDPG]
Let $G = (V, E)$ with adjacency matrix $A$ be sampled from the homogeneous SBM with two communities such that within-community edge probability $p$ and between-community edge probability $q$ where $p > q$. Let community 1 have $n_1$ vertices and community 2 have $n_2$ vertices such that $n_1 + n_2 = n$. Without loss of generality, organize $P$ and $A$ such that the $kl^{th}$ block represents edges between communities $k$ and $l$. Then $P = \begin{bmatrix} P^{(11)} & P^{(12)} \\ P^{(21)} & P^{(22)} \end{bmatrix}$ where each block is a constant value, e.g., $P^{(11)}_{ij} = p$. One RDPG representation of this SBM is:

@@

Given sufficiently large sample size $n$, the scaled ASE of affinity matrix $A$ drawn from a RDPG or GRDPG will asymptotically approach the original latent positions $X$ with probability 1, up to a linear transformation (orthogonal transformation for the RDPG, a composition of an orthogonal and scale transformations for the GRDPG). Thus if $X$ consists of points that lie on subspaces of $\mathbb{R}^d$, then both the scaled and unscaled ASE of $A \sim \text{RDPG}(X)$ or $A \sim \text{GRDPG}(X)$ will consist of points that lie near subspaces, with some noise that almost surely goes to $0$ as $n \to \infty$, motivating ASE followed by SSC as an asymptotically consistent method for community detection. The Popularity Adjusted Block Model (PABM) \cite{307cbeb9b1be48299388437423d94bf1} is a generative graph model with underlying communities such that each community lies on a subspace. \citet{noroozi2019estimation} showed that SSC is able to recover the subspaces and therefore perform community detection for the PABM given $P = X I_{p, q} X^\top$, the edge probability matrix, rather than $A$, the adjacency matrix. Combining the results of \citeauthor{rubindelanchy2017statistical} and \citeauthor{jmlr-v28-wang13}, it should be possible to recover the communities using $A$ as well.

@@

\citet{trosset2020learning} showed that the ASE of a RDPG can be used to recover one-dimensional manifolds. Suppose $f : [0, 1] \mapsto \mathcal{X}$ such that $f$ is smooth and $\mathcal{X}$ represents a curve or one-dimensional manifold in $\mathbb{R}^d$. If $t_1, ..., t_n \stackrel{iid}{\sim} F$ such that $F$ has support $[0, 1]$, the latent positions are $x_i = f(t_i)$ with $y_i$ is its corresponding point in the scaled ASE, and $d_{\epsilon}(\cdot, \cdot)$ is the shortest path distance of an $\epsilon$-neighborhood graph. Under certain mild conditions, the shortest path distances of the $\epsilon$-neighborhood graph of the ASE approaches the arc lengths along $f$:

@@

As discussed in \S 2.1, all Bernoulli graph models can be expressed as a RDPG or GRDPG model, and in particular, the (associative) SBM is a RDPG with a very specific structure in the latent space. A similar result has been shown for the DCBM. We will now extend this to the PABM.

@@

It is trivial to show that the PABM, as well as all graphs such that the adjacency matrix is drawn such that $A_{ij} \sim Bernoulli(P_{ij})$, is a special case of the GRDPG. It can also be shown that the latent positions of the PABM under the GRDPG framework consists of $K$ $K$-dimensional subspaces in $\mathbb{R}^{K^2}$. While there is no unique latent configuration $X$ such that $X X^\top = P$, the edge probability $P$ for the PABM, they all have this subspace structure, and one in particular consists of *orthogonal* subspaces.

@@

In Theorem \ref{theorem2}, we showed that a possible latent configuration for a $K$-community PABM under the GRDPG framework consists of latent positions in $\mathbb{R}^{K^2}$ such that each community corresponds to a $K$-dimensional subspace such that each subspace is orthogonal to the others.

@@

If $\hat{V}$ is the *unscaled* ASE of $A$, then results from  \citeauthor{rubindelanchy2017statistical} imply $n \hat{V} \hat{V}^\top \stackrel{a.s.}{\to} n V V^\top$. Then for vertices $i$ and $j$ belonging to separate communities, the $ij$^th^ entry of $n \hat{V} \hat{V}^\top$ approaches 0 with probability 1:

@@

In addition to OSC, since the communities are subspaces in the latent space, we can leverage existing methods for subspace clustering. Of particular interest is Sparse Subspace Clustering (SSC), which is performed by solving an optimization problem for each observed point in a sample. Given $X \in \mathbb{R}^{n \times d}$ with vectors $x_i^\top \in \mathbb{R}^d$ as rows of $X$, the optimization problem $c_i = \min\limits_{c} \|c\|_1$ subject to $x_i = X_{-i} c$ and $c^{(i)} = 0$ is solved for each $i \in [n]$. The solutions are collected into matrix $C = \begin{bmatrix} c_1 & \cdots & c_n \end{bmatrix}^\top$ to construct affinity matrix $B = |C| + |C^\top|$. If each $x_i$ lie perfectly on one of $K$ subspaces, $B$ is sparse such that $B_{ij} = 0$ $\forall x_i, x_j$ belonging to different subspaces. Then $B$ can describe a graph with at least $K$ disjoint subgraphs, and if the number of subgraphs is exactly $K$, each subgraph maps onto a subspace.

@@

\begin{remark} 
In practice, a noisy sample $X$ often does not obey SDP. 
In such cases, $B$ is treated as an affinity matrix for a graph which 
is then partitioned into $K$ subgraphs to obtain the clustering. On the other 
hand, if $X$ does obey the SDP, $B$ describes a graph 
with at least $K$ disconnected subgraphs. Ideally, when SDP holds, 
there are exactly $K$ subgraphs which map to each subspace, 
but it could be the case that some of the subspaces are represented by 
multiple disconnected subgraphs. SDP is contingent 
on choosing a sufficiently large sparsity parameter $\lambda$. 
\end{remark}

Since every ASE of the PABM consists of subspaces and as $n \to \infty$ each point of the ASE approaches its subspace almost surely, SSC should also work for PABM community detection. Combining this with the results by \citeauthor{jmlr-v28-wang13}, which state that if the points lie sufficiently close to their respective subspaces and the cosine of the angles between subspaces is sufficiently small, SDP will hold. We show that the unscaled ASE exhibits exactly these conditions for sufficiently large $n$.

\begin{theorem}
\label{theorem5}
Let $P_n$ describe the edge probability matrix of the PABM with 
$n$ vertices, and let $A_n \sim \Bernoulli(P_n)$.  Let $\hat{V}_n$ be the 
matrix of eigenvectors of $A_n$ corresponding to the $K (K + 1) / 2$ most
positive and $K (K - 1) / 2$ most negative eigenvalues. Then 
$\exists \lambda > 0$ and $N \in \mathbb{N}$ such that when $n > N$, 
$\sqrt{n} \hat{V}_n$ obeys the subspace detection property with probability 1.
\end{theorem}

@@

In the previous sections, we connected well-known and highly structured generative graph models to the RDPG and GRDPG to show that highly structured latent configurations generate graphs consistent with these models: The latent space for the SBM consists of $K$ point masses, the latent space for the DCBM consists of $K$ rays emanating from the origin, and the latent space for the PABM consists of $K$ $K$-dimensional subspaces. In the following sections, we explore additional structured latent configurations corresponding to community structure and develop methods for community detection based on the consistency of the ASE and the structural forms of the latent configurations.

@@

@@

If we extend this example such that $n_1$ points are sampled uniformly from the segment $f_1(t) = (t, 0)$ and $n_2$ points are sampled uniformly from the segment $f_2(t) = (t, a)$ for $t \in [0, 1]$, then a sample of size $N(\delta, a)$ is sufficient to satisfy:

>>>>

options(xtable.comment = FALSE, 
        xtable.table.placement = 'H')

import::from(magrittr, `%>%`)
library(ggplot2)
```

@@

Graph and network data have become increasingly widespread in various fields including sociology, neuroscience, biostatistics, and computer science. This has resulted in various challenges for researchers who rely on traditional statistical and machine learning methods, many of which are incompatible with graph data and instead require the data to exist as feature vectors in Euclidean space. Such challenges often involve clustering and community detection, which are often the goal of graph data analysis. Common clustering methods typically involve calculating some central or representative point for each cluster around which the data belonging to that cluster lie (e.g., Lloyd's algorithm for $K$-means clustering \cite{1056489}, Gaussian Mixture Models \cite{doi:10.1198/016214502760047131}). Because these methods involve computing summary statistics within each cluster, such as the sample average, they cannot be applied directly to graphs, necessitating methods for transforming the graph data into feature vectors.

@@

The aim of our research is to develop consistent community detection techniques under the RDPG and GRDPG frameworks. First, we explore existing generative graph models with underlying community structures that can be inferred by connecting these models to the RDPG or GRDPG. Then we explore other latent structures or mixture distributions in the latent space that induce graphs for which consistent community detection is possible.

@@

Let $G = (V, E)$ be an undirected, unweighted graph with no self-loops and $n$ vertices. Denote $A \in \{0, 1\}^{n \times n}$ as the adjacency matrix for $G$ such that $A_{ij} = 1$ if there exists an edge between vertices $i$ and $j$ and $A_{ij} = 0$ otherwise. Because $G$ is symmetric and contains no self-loops, $A_{ij} = A_{ji}$ and $A_{ii} = 0$ for $i, j \in [n]$. We further restrict our analyses to independent Bernoulli graphs. Let $P \in [0, 1]^{n \times n}$ be a symmetric matrix of edge probabilities. Graph $G$ is sampled from $P$ by drawing $A_{ij} \indep \Bernoulli(P_{ij})$ for each $1 \leq i < j \leq n$ ($A_{ji} = A_{ij}$ and $A_{ii} = 0$). Finally, we denote $X = \begin{bmatrix} x_1 & \cdots & x_n \end{bmatrix}^\top \in \mathbb{R}^{n \times d}$ as the sample $x_1, ..., x_n \in \mathbb{R}^d$ and $z_1, ..., z_n \in [K]$ as their corresponding (hidden) labels.

@@

Generative models for independent Bernoulli graphs involve defining the edge probability matrix $P$ whose $ij$^th^ entry is the probability of an edge between vertices $i$ and $j$ for each $i, j \in [n]$. In order to motivate community detection methods, we restrict the generative model such that for each pair of vertices, the probability of an edge between the vertices is conditioned on their labels. One such model is the Stochastic Block Model (SBM) \cite{doi:10.1080/0022250X.1971.9989788}: Given $K$ communities and each vertex belonging to one community, the SBM restricts $P$ to $K (K + 1) / 2$ unique entries such that $P_{ij} = p_{z_i z_j}$ where $p_{kl} = p_{lk}$ is the probability of an edge between each vertex in community $k$ to each vertex in community $l$. The homogeneous SBM further restricts $P$ to two unique entries: $P_{ij} = p$ if $z_i = z_j$ and $P_{ij} = q$ otherwise. Several generalizations of the SBM have been introduced since, including the Degree Corrected Block Model (DCBM) and the Popularity Adjusted Block Model (PABM). Like the SBM, these models involve imposing some restriction on $P$ based on community labels (and possibly other factors).

@@

The structure of the RDPG and GRDPG provides a straightforward method for recovery of the latent positions via spectral decomposition.

@@

It is straightforward to show that all Bernoulli graphs with positive semidefinite $P$ are special cases of the RDPG, which is a special case of the GRDPG, and all graphs generated by $P$ are special cases of the GRDPG. This includes the SBM, DCBM, and PABM. In the following example, we show that under the RDPG framework, the latent configuration that induces the SBM takes on a very particular form.

\begin{example}[Connecting the SBM to the RDPG]
Let $G = (V, E)$ with adjacency matrix $A$ be sampled from the SBM with two communities for which the within-edge probabilities are $p$ and $q$ for communities 1 and 2 respective, and the between-community edge probability is $r$, with $p q > r^2$. Let community 1 have $n_1$ vertices and community 2 have $n_2$ vertices such that $n_1 + n_2 = n$. Without loss of generality, organize $P$ and $A$ such that the $kl^{th}$ block represents edges between communities $k$ and $l$. Then $P = \begin{bmatrix} P^{(11)} & P^{(12)} \\ P^{(21)} & P^{(22)} \end{bmatrix}$ where each block is a constant value, e.g., $P^{(11)}_{ij} = p$. One RDPG representation of this SBM is:

@@

@@

\citet{trosset2020learning} showed that the ASE of a RDPG can be used to recover one-dimensional manifolds. Suppose $f : [0, 1] \mapsto \mathcal{X}$ such that $f$ is smooth and $\mathcal{X}$ represents a curve or one-dimensional manifold in $\mathbb{R}^d$. If $t_1, ..., t_n \iid F$ such that $F$ has support $[0, 1]$, the latent positions are $x_i = f(t_i)$ with $y_i$ is its corresponding point in the scaled ASE, and $d_{\epsilon}(\cdot, \cdot)$ is the shortest path distance of an $\epsilon$-neighborhood graph. Under certain mild conditions, the shortest path distances of the $\epsilon$-neighborhood graph of the ASE approaches the arc lengths along $f$:

@@

As discussed in \S 2.1, all Bernoulli graph models can be expressed as a RDPG or GRDPG model, and in particular, the (associative) SBM is a RDPG with a very specific structure in the latent space. A similar result has been shown for the DCBM \cite{lyzinski2014}. We have also extended this to the PABM. In \S 3.3.1, we show that the PABM is equivalent to the GRDPG model for which the communities correspond to subspaces in the latent configuration. We further show that while the latent configuration is not unique, there exists one in particular for which the subspaces are orthogonal. This leads to two straightforward methods for community detection, one involving computing inner products in the ASE and another which is a slight modification of an existing algorithm for subspace clustering. Finally, we will briefly explore alternative, non-spectral-based methods for community detection in the ASE involving Expectation Maximization, MCMC sampling, and Mean Field Variational Inference.

@@

It is straightforward to show that the PABM, as well as all graphs such that the adjacency matrix is drawn such that $A_{ij} \indep Bernoulli(P_{ij})$, is a special case of the GRDPG. It can also be shown that the latent positions of the PABM under the GRDPG framework consists of $K$ $K$-dimensional subspaces in $\mathbb{R}^{K^2}$. While there is no unique latent configuration $X$ such that $X X^\top = P$, the edge probability $P$ for the PABM, they all have this subspace structure, and one in particular consists of *orthogonal* subspaces.

@@

In Theorem \ref{theorem2}, we showed that a possible latent configuration for a $K$-community PABM under the GRDPG framework consists of vectors in $\mathbb{R}^{K^2}$ such that each community corresponds to a $K$-dimensional subspace and each subspace is orthogonal to the others.

@@

If $\hat{V}$ is the *unscaled* ASE of $A$, then results from  \citet{rubindelanchy2017statistical} imply $n \hat{V} \hat{V}^\top \stackrel{a.s.}{\to} n V V^\top$. Then for vertices $i$ and $j$ belonging to separate communities, the $ij$^th^ entry of $n \hat{V} \hat{V}^\top$ approaches 0 with probability 1:

@@

Since the communities are subspaces in the latent space, we can also use existing methods for subspace clustering on the ASE. Of particular interest is Sparse Subspace Clustering (SSC), which is performed by solving an optimization problem for each observed point in a sample. Given $X \in \mathbb{R}^{n \times d}$ with vectors $x_i^\top \in \mathbb{R}^d$ as rows of $X$, the optimization problem $c_i = \min\limits_{c} \|c\|_1$ subject to $x_i = X_{-i} c$ and $c^{(i)} = 0$ is solved for each $i \in [n]$. The solutions are collected into matrix $C = \begin{bmatrix} c_1 & \cdots & c_n \end{bmatrix}^\top$ to construct affinity matrix $B = |C| + |C^\top|$. If each $x_i$ lie perfectly on one of $K$ subspaces, $B$ is sparse such that $B_{ij} = 0$ $\forall x_i, x_j$ belonging to different subspaces. Then $B$ can describe a graph with at least $K$ disjoint subgraphs, and if the number of subgraphs is exactly $K$, each subgraph maps onto a subspace.

@@

\begin{remark} 
In practice, a noisy sample $X$ often does not obey SDP. 
In such cases, $B$ is treated as an affinity matrix for a graph which 
is then partitioned into $K$ subgraphs to obtain the clustering. On the other 
hand, if $X$ does obey the SDP, $B$ describes a graph 
with at least $K$ disconnected subgraphs. Ideally, when SDP holds, 
there are exactly $K$ subgraphs which map to each subspace, 
but it could be the case that some of the subspaces are represented by 
multiple disconnected subgraphs.
\end{remark}

Since every ASE of the PABM consists of subspaces and as $n \to \infty$ each vector of the ASE approaches its subspace uniformly \cite{rubindelanchy2017statistical}, SSC is also able to perform community detection for the PABM. It has been shown by \citet{jmlr-v28-wang13} that if the points lie sufficiently close to their respective subspaces and the cosine of the angles between subspaces is sufficiently small, SDP will hold. We now state that the unscaled ASE of the PABM exhibits exactly these conditions for sufficiently large $n$.

\begin{theorem}
\label{theorem5}
Let $P_n$ describe the edge probability matrix of the PABM with 
$n$ vertices, and let $A_n \sim \Bernoulli(P_n)$.  Let $\hat{V}_n$ be the 
matrix of eigenvectors of $A_n$ corresponding to the $K (K + 1) / 2$ most
positive and $K (K - 1) / 2$ most negative eigenvalues. Then 
$\exists \lambda > 0$ and $N < \infty$ such that when $n > N$, 
$\sqrt{n} \hat{V}_n$ obeys the subspace detection property with probability 1.
\end{theorem}

#### Alternative Approaches to Community Detection

So far, we connected the PABM to the GRDPG and used this to motivate community detection methods based on the ASE of the adjacency matrix sampled from the PABM. In this section, we will explore non-spectral methods for community detection.

Denoting $\{\lambda_{ik}\}$ as the scalar popularity parameters for the PABM such that $\lambda^{(kl)}$ is the vector of $\lambda_{jl}$ terms for which vertex $j$ is in community $k$, we can write the likelihood for the PABM:

$$p(A | z, \{\lambda_{ik}\}) = 
\prod_{i < j} (\lambda_{i z_j} \lambda_{j z_i})^{A_{ij}} 
(1 - \lambda_{i z_j} \lambda_{j z_i})^{1 - A_{ij}}$$

\begin{equation}
= \prod_{i < j} \prod_k^K \prod_l^K 
(\lambda_{il} \lambda_{jk})^{A_{ij} z_{ik} z_{jl}} 
(1 - \lambda_{il} \lambda_{jk})^{(1 - A_{ij}) z_{ik} z_{jl}}
\end{equation}

where $z_{ik} = I(Z_i = k)$.

The log-likelihood is

\begin{equation}
\log p = \sum_{i < j} \sum_k \sum_l z_{ik} z_{jl} 
(A_{ij} \log \lambda_{il} \lambda_{jk} + 
(1 - A_{ij}) \log (1 - \lambda_{il} \lambda_{jk}))
\end{equation}

While direct maximization of the likelihood or log-likelihood is NP-complete, it is possible to apply an Expectation Maximization (EM) algorithm to this problem. To set this up,

@@

In the previous sections, we connected well-known and highly restricted generative graph models to the RDPG and GRDPG to show that highly structured latent configurations generate graphs consistent with these models: The latent space for the SBM consists of $K$ point masses, the latent space for the DCBM consists of $K$ rays emanating from the origin, and the latent space for the PABM consists of $K$ $K$-dimensional subspaces. In the following sections, we explore additional structured latent configurations corresponding to community structure and develop methods for community detection based on the consistency of the ASE and the structural forms of the latent configurations.

@@

```{r, fig.cap = 'Points sampled uniformly on two parallel unit length line segments', fig.height = 1}
set.seed(1)

n1 <- 2 ** 5
n2 <- 2 ** 5
n <- n1 + n2

a <- .1

X <- cbind(runif(n1, 0, 1), rep(0, n1))
Y <- cbind(runif(n2, 0, 1), rep(a, n2))

data.matrix <- rbind(X, Y)
z <- c(rep(1, n1), rep(2, n2))

as.data.frame(data.matrix) %>% 
  dplyr::mutate(label = factor(z)) %>% 
  ggplot() + 
  geom_segment(aes(x = 0, xend = 1, y = 0, yend = 0)) + 
  geom_segment(aes(x = 0, xend = 1, y = a, yend = a)) + 
  geom_point(aes(x = V1, y = V2, colour = label)) + 
  labs(x = NULL, y = NULL, colour = NULL) + 
  guides(colour = FALSE) + 
  xlim(-.1, 1.1) + 
  ylim(-a, 2 * a) + 
  scale_colour_brewer(palette = 'Set1') + 
  coord_fixed() + 
  ggthemes::theme_few() + 
  theme(axis.text = element_blank(),
        axis.ticks = element_blank())
```

```{r, eval = FALSE}
source('~/dev/pabm-grdpg/functions.R')

P <- data.matrix %*% t(data.matrix)
A <- draw.graph(P)

qgraph::qgraph(A, groups = factor(z), layout = 'spring')
```

```{r, eval = FALSE}
eigen.A <- eigen(A)
ind <- seq(2)
U <- eigen.A$vectors[, ind]
S <- diag(sqrt(abs(eigen.A$values[ind])))
Z <- U %*% S
pairs(Z, asp = 1, col = z)
```

@@

If we extend this example such that $n_1$ points are sampled uniformly from the segment $f_1(t) = (t, 0)$ and $n_2$ points are sampled uniformly from the segment $f_2(t) = (t, a)$ for $t \in [0, 1]$, then a sample of size $\min(n_1, n_2) \geq N(\delta, a)$ is sufficient to satisfy:
